{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-12-02 documents/fluorescence.tex
Wording
osmotically-stressed phage doesn't do it either
writing!
math

@@

Performance of this arrangement was satisfactory. A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately \pm 1500 counts.

>>>>

virus-specific

hemagglutinin test

bleaching was not obviously an issue

A white LED with a high color-rendering index (DK) seemed to have more power in the passband; however, green leakage around the filter was too strong.

Unlike gels or plastic-glass sandwiches as used by Tiffen, thin-film filters have the disadvantage that the pass-band depends greatly on the angle of incidence.

$$\lambda = \lambda \sqrt{1-sin(\theta)^2}$$

The wavelength shifts shorter (bluer) as $\theta$ increases.

This isn't an issue for the excitation filter, but is an issue for the.

Since the LEDs and flurophore emissions are not naturally collimated, this poses a little bit of an issue.
The microscope objective seems to provide sufficient collimation for the emission filter.

The Edmund filter was unmounted glass. Also, these thin-film filters do not extend to the edge of the glass. Edge-blankening ("inked") fil

The LED was about 3 cm away, and put through a ~3 mm aperture. The output from the filter was directly into the 1 mm fiber, itself improving the bandpass.

The 10 nm FWHM emission filter is much narrower than professional GFP filters, especially the super-wide edge-pass ones; a lot of photons are lost that way. However, it's still more than sufficient.

@@

Performance of this arrangement was satisfactory. A 10-second integration time, with, produced a background fluorescence signal of ~1500 counts, with per-sample stability of approximately \pm 1500 counts. The

### 2020-12-02 documents/lessons_learned.tex
math

@@

Papers only carry the scientific heritage that their authors saw fit to include in the references section.

@@

Minor errors in . Reproducible coding helps, but it would be much better if we had used standard software engineering best practices; red-teaming, unit testing on randomly generated data, etc. It might also be helpful if the data itself are blinded against randomly generated controls - in many cases that's not possible, but it might be useful in some circumstances.

@@

@@

Manually taking notes tended to disrupt the flow of testing; and in any case, just noting "SIR filter has appropriate phase response" is almost useless. What {\it was} the phase response? Plot it!

@@

I think this is a good general rule: record as much detail automatically as possible

@@

@@

@@

There's also a very neat thing that seems to be common in computational biology, but which doesn't seem popular in other fields. After an algorithm or software tool is written (and the source published separately), a simple CGI frontend is written around it and hosted on the university's servers. eLNemo and the CHARMMing web interface are advanced examples of this. This way, anyone with an input file can get results without futzing around with installation.

@@

In one example in this project, many hours were wasted because the enamel insulation on a bodge wire had not burned off completely in the solder joint, leading to a high-impedance connection.

@@

The ability to almost immediately compare simulation to experiment was essential.

@@

but, some months later, it was found that he was *right* - absolutely right.

>>>>

It is interesting to think about the meta-issues surrounding this project. Beta-glo assay, not a few kilometers away the food bank ran out of food and people were not able.

This one was taught to me by Yuriy!

We were trying to write a pre-baked math worksheet into Wolfram Mathematica.

It is useful to first strictly implement precisely as written, and only when all parts are operational and understood, begin modifying for your own use.

This is common practice in many fields, but hadn't occurred to me for math.

@@

Papers only carry the scientific heritage that their authors saw fit to include in the references section, and only provide the context included in the "introduction".

@@

We often came across a situation in which minor errors in software,  would completely change the conclusion of our results.

Reproducible coding helps, but it would be much better if we had used standard software engineering best practices; red-teaming, unit testing on randomly generated data, etc. It might also be helpful if the data itself are blinded against randomly generated controls - in many cases that's not possible, but it might be useful in some circumstances.

@@

It may be useful to make explicit to the reader where particular sensitivities - high gradients of conclusion against some factor - might exist in your research.

@@

Manually taking notes tended to disrupt the flow of testing; and in any case, just noting "SIR filter has appropriate phase response" is almost useless. What {\it was} the phase response? Plot it, and upload it!

@@

I think this is a good general rule: record as much detail as automatically as possible

@@

Dill

@@

Honestly, this might already account for a difference in productivity between, say, Python, and C++. the package manager.

@@

There's also a very neat thing that seems to be common in computational biology, but which doesn't seem popular in other fields. After an algorithm or software tool is written (and the source published separately), a simple CGI frontend is written around it and hosted on the university's servers. eLNemo and the CHARMMing web interface are advanced examples of this. This way, anyone with an input file can get results without futzing around with installation, at least for the few decades that the servers are maintained.

@@

In one example in this project, many hours were wasted because the enamel insulation on a bodge wire had not burned off completely in a solder joint, leading to a high-impedance connection.

@@

The ability to almost immediately compare simulation to experiment was of great use almost everywhere in this project. This hybrid, "lockstep" approach between theory, simulation, and practice works, I think, extremely well. Even if all these intermediate experiments fail, the mere process of setting up an experiment offers you insight - and forces you to persue leads - which would not otherwise have been gained. Is it better than, say, spending a year carefully establishing the theory behind an experiment, and then doing one? I'm not sure. Other teams have had great success with this.

@@

but, some months later, it was found that he was *right* - absolutely right. This was a grave error in management!
